\subsection{2-2}
%\begin{enumerate}[itemsep=0.5em, align=right, leftmargin=2.5em]
\begin{enumerate}[leftmargin=*]
    \item We need to show that the elements in $A'$ forms a permutation
        of the elements in $A$.
    \item \textbf{Loop invariant:} $A[j]=min{A[j\twodots \attrib{A}{length}]}$
        and the subarray $A[j\twodots \attrib{A}{length}]$ is a permutation of
        the elements in $A[j\twodots \attrib {A}{length}]$ at the time when
        the loop started. \\
        \textbf{Initialization:} On initialization, subarray
        $A[j\twodots \attrib{A}{length}]$ only contains one element, so its
        the smallest element in the subarray. \\
        \textbf{Maintenance:} The only possible operation to the subarray is
        exchange $A[j]$ and $A[j-1]$ when $A[j]<A[j-1]$. Since $A[j]$ is the
        smallest element in $A[j\twodots \attrib{A}{length}]$, if the exchange
        happens, $A[j-1]$ would become the smallest element in $A[j-1\twodots
        \attrib{A}{length}]$. Meanwhile, since subarray
        $A[j\twodots \attrib{A}{length}]$ is a permutation of the elements in
        $A[j\twodots \attrib{A}{length}]$ at the time the loop started, after
        exchanging $A[j]$ and $A[j-1]$, $A[j-1\twodots \attrib{A}{length}]$ is
        still a permutation of the elements that were in $A[j-1\twodots]$
        at the time the loop started. \\
        \textbf{Termination:} Since $j$ decreases by $1$ after each iteration,
        the condition that causes the loop terminate is $j=i$. By the state of
        the loop invariant, $A[i]=min{A[i\twodots \attrib {A}{length}]}$, and
        subarray $A[i\twodots \attrib{A}{length}]$ is a permutation of the
        elements that were in $A[i\twodots \attrib {A}{length}]$ at the time
        the loop started.
    \item \textbf{Loop invariant:} Subarray $A'[1\twodots i-1]$ contains $i-1$
        smallest elements come from array $A[1\twodots \attrib{A}{length}]$
        and in ordered manner. \\
        \textbf{Initialization:} Piror to the first iteration of the outer
        \textbf{for} loop, $i=1$, so there is no element in $A'[1\twodots i-1]$,
        the loop invariant holds. \\
        \textbf{Maintenance:} Since $A'[1\twodots i-1]$ is the $i-1$ smallest
        elements from $A[1\twodots \attrib{A}{length}]$, after the execution
        of the inner \textbf{for} loop, which makes $A'[i]$ the smallest
        element of subarray $A[i\twodots \attrib[A][length]]$, and the values
        in the subarray all come from $A[1\twodots \attrib{A}{length}]$, hence
        subarray $A'[1\twodots i]$ contains the $i$ smallest elements in
        $A[1\twodots \attrib{A}{length}]$. \\
        \textbf{Termination:} The loop terminates when $i$ reaches
        $\attrib{A}{length}$, by the state of the loop invariant,
        $A'[1\twodots \attrib{A}{length-1}]$ contains $\attrib{A}{length-1}$
        smallest elements of $A[1\twodots \attrib{A}{length}]$, moreover, since
        $A[\attrib{A}{length}]$ is the only element in the remaining subarray,
        therefore it is the largest element of
        $A[1\twodots \attrib{A}{length}]$. In conclusion, array
        $A'[1\twodots \attrib{A}{length}]$ is a permutation of
        $A[1\twodots \attrib{A}{length}]$ but in sorted manner.
    \item The worest case running time of the $\proc{Bubblesort}$
        is:
        \begin{displaymath}
            \sum_{i=1}^{\attrib{A}{length}-1}
            (n-i+1)=\frac{n^2}{2}
            =\Theta(n^2)
        \end{displaymath}
        It is the same as the worest case running time of insertion sort.
\end{enumerate}
